A Constraint Solving Approach to Parikh Images of Regular Languages

### 2022-11-28 main.tex
Its ALIGNED
rename MATHS, fix alignment in examples
Align 2nd example
Some uncommitted work, apparently

  % SUBSUME
  \Subsume &
  \inferrule{\SomeInequalities,\SomeClause}{\Connected(\Automaton, \Filter), \SomeInequalities, \SomeClause} &
  \Split{} and \Propagate{} cannot be applied \\
  \bottomrule
  \end{tabular}
  \caption{Derivation rules for one automaton.}\label{tbl:rules:single}
\end{table}
We use the symbolic function $\FlowEq(\Automaton, \Filter)$ that generates a set
of existentially quantified linear inequalities with the following definition,
where we assign fresh, existentially quantified variables to
$\FinalStateVar_\State, \Filter(\Transition)$ for every $\State \in
\AcceptingStates, \Transition \in \Transitions$:
\[
\begin{aligned}
  & \FlowEq(\Automaton, \Filter) = \sum\limits_{\State \in \AcceptingStates} \FinalStateVar_\State = 1 \land \AndComp{\State \in \States}{\In(\State, \Filter) - \Out(\State, \Filter)} = \Sink(\State) \land
  \AndComp{\State \in \AcceptingStates}{\FinalStateVar_\State \geq 0}\\
  & \Sink(\State) = 0 \text{ if } \State \not\in \AcceptingStates, \FinalStateVar_\State \text{ otherwise.} \\
  & \In(\State, \Filter) = \StartFlow(\State) + \sum_{\Transition \in \FromLabelTo{\State'}{}{\State}} \Filter(\Transition)\\
  & \StartFlow(\State)  = 1 \text{ if } \State = \InitialState, \text{ otherwise $0$.} \\
  & \Out(\State, \Filter) = \sum_{\Transition \in \FromLabelTo{\State}{}{\State'}} \Filter(\Transition)
\end{aligned}
\]

@@

\begin{figure}[ht]
  We define $\Filter$ and $\FlowEq(\AcaOrBc{}, \Filter)$ as in the following two
  equations, and then apply \EquationReasoning{} (under the implicit assumption
  that every RHS is $\geq 0$) to obtain the equivalent third definition :
  \begin{minipage}[b]{0.3\linewidth}
    \begin{equation*}
      \begin{aligned}
        & \Filter(\FromLabelTo{S}{a}{A}) & = \TransitionVar_1 \\
        & \Filter(\FromLabelTo{S}{b}{B}) & = \TransitionVar_2 \\
        & \Filter(\FromLabelTo{A}{c}{A})  & = \TransitionVar_3  \\
        & \Filter(\FromLabelTo{B}{b}{S}) & = \TransitionVar_4 \\
        & \Filter(\FromLabelTo{A}{a}{F}) & = \TransitionVar_5 \\
        & \Filter(\FromLabelTo{B}{c}{F}) & = \TransitionVar_6 \\
      \end{aligned}
    \end{equation*}    
  \end{minipage}
  \hspace{0.5cm}
  \begin{minipage}[b]{0.3\linewidth}
    \begin{equation*}
      \begin{aligned}
        % S
        &  \TransitionVar_4 = \TransitionVar_5 + \TransitionVar_2 - 1 \\
        % A
        & \TransitionVar_1 = \TransitionVar_5 \\
        % B
        & \TransitionVar_2 = \TransitionVar_4 + \TransitionVar_6 \\
        % F
        & \TransitionVar_5 + \TransitionVar_6 = \FinalStateVar_1 \\
        & \FinalStateVar_1 = 1 \\
      \end{aligned}  
    \end{equation*}    
  \end{minipage}
  \begin{minipage}[b]{0.3\linewidth}
    \begin{equation*}
      \begin{aligned}
        & \Filter(\FromLabelTo{S}{a}{A}) & = 1 - \TransitionVar_6 \\
        & \Filter(\FromLabelTo{S}{b}{B}) & = \TransitionVar_4 + \TransitionVar_6 \\
        & \Filter(\FromLabelTo{A}{c}{A})  & = \TransitionVar_3  \\
        & \Filter(\FromLabelTo{B}{b}{S}) & = 2\TransitionVar_6 + \TransitionVar_4 \\
        & \Filter(\FromLabelTo{A}{a}{F}) & = 1 - \TransitionVar_6 \\
        & \Filter(\FromLabelTo{B}{c}{F}) & = \TransitionVar_6 \\
      \end{aligned}
    \end{equation*}    
  \end{minipage}
  \caption{Equivalences defining $\Filter$ and $\FlowEq(\AcaOrBc{}, \Filter)$
  respectively.}\label{fig:example:single:equivalences}
  \end{figure}

\begin{figure}
  \centering
\begin{prooftree}
  \hypo[]{
    \begin{matrix}
      1 - \TransitionVar_6 = 0 \land \\
      \TransitionVar_6 = 1 \land \\
      \TransitionVar_4 + 1 > 0 \land \\
      \TransitionVar_3 = 0 \land \\
      2 + \TransitionVar_4 > 0 \land \\
      k = 1 + \TransitionVar_4 
    \end{matrix}
  }
  \infer1[\Subsume{}]{
    \begin{matrix}
      \Connected(\AcaOrBc{}, \Filter) \land \\
      1 - \TransitionVar_6 = 0 \land \\
      \TransitionVar_6 = 1 \land \\
      \TransitionVar_4 + 1 > 0 \land \\
      \TransitionVar_3 = 0 \land \\
      2 + \TransitionVar_4 > 0 \land \\
      k = 1 + \TransitionVar_4 
    \end{matrix}
  }
  \infer1[\Propagate]{
    \begin{matrix}
      \Connected(\AcaOrBc{}, \Filter) \land \\
      1 - \TransitionVar_6 = 0 \land \\
      \TransitionVar_6 = 1 \land \\
      \TransitionVar_4 + 1 > 0 \land \\
      \TransitionVar_3 \geq 0 \land \\
      2 + \TransitionVar_4 \geq 0 \land \\
      2k = 2 + 2\TransitionVar_4 + \TransitionVar_3
    \end{matrix}
  }
  \infer1[\EquationReasoning{}]{
    \begin{matrix}
      \Connected(\AcaOrBc{}, \Filter) \land \\
      1 - \TransitionVar_6 = 0 \land \\
      2k = 1 + 2\TransitionVar_4 + \TransitionVar_3 + \TransitionVar_6
    \end{matrix}
  }
  % BRANCH:  = 0'
  \hypo{
    \begin{matrix}
      \TransitionVar_3 > 0 \land \\
      \TransitionVar_6 = 0 \land \\
      2\TransitionVar_6 + \TransitionVar_4 = 0 \land \\
      1 - \TransitionVar_6 > 0 \land \\
      2k = 1 + \TransitionVar_3
    \end{matrix}
  }
  \infer1[\Subsume{}]{
    \begin{matrix}
      \Connected(\AcaOrBc{}, \Filter) \land \\
      \TransitionVar_3 > = 0 \land \\
      \TransitionVar_6 = 0 \land \\
      2\TransitionVar_6 + \TransitionVar_4 = 0 \land \\
      1 - \TransitionVar_6 > 0 \land \\
      2k = 1 + \TransitionVar_3
    \end{matrix}
  }
  \infer1[\EquationReasoning{}]{
    \begin{matrix}
      \Connected(\AcaOrBc{}, \Filter) \land \\
      \TransitionVar_6 = 0 \land \\
      1 - \TransitionVar_6 > 0 \land \\
      2\TransitionVar_6 + \TransitionVar_4 = 0\\
      2k = 1 + 2\TransitionVar_4 + \TransitionVar_3
    \end{matrix}
  }
  \infer1[\Propagate{}]{
    \begin{matrix}
      \Connected(\AcaOrBc{}, \Filter) \land \\
      \TransitionVar_6 = 0 \land \\
      1 - \TransitionVar_6 > 0 \land \\
      2k = 1 + 2\TransitionVar_4 + \TransitionVar_3
    \end{matrix}
  }
  \infer1[\EquationReasoning{}]{
    \begin{matrix}
      \Connected(\AcaOrBc{}, \Filter) \land \\
      1 - \TransitionVar_6 > 0 \land \\
      2k = 1 + 2\TransitionVar_4 + \TransitionVar_3 + \TransitionVar_6
    \end{matrix} % BRANCH: > 0
  } % SPLIT
  \infer2[\Split{} $1 - \TransitionVar_6$]{ \Connected(\AcaOrBc{}, \Filter) \land 2k = 1 + 2\TransitionVar_4 + \TransitionVar_3 + \TransitionVar_6 }
  \infer1[\EquationReasoning{}]{
    \Connected(\AcaOrBc{}, \Filter) \land
    2k + 1 =
    \sum\limits_{\Transition \in \Transitions} (\Transition \mapsto 1)(\Label) \cdot \Filter(\Transition)
  }
  \infer1[\Expand{}]{\Image{}_{\AcaOrBc{}, \Transition \mapsto 1}(\Filter, 2k + 1)}
\end{prooftree}
\caption{A derivation for \Calculus{} computing odd lengths in $\AcaOrBc{}$.}\label{fig:derivation:single}
\end{figure}

@@

In the interest of space, we refer back to
\cref{fig:example:single:equivalences} for the definitions of $\Filter$ for
$\AcaOrBc$ and only define $\Filter$ for $\SomethingCSomething{}$ after
substitutions as follows. Note the expansion of the $\Sigma$ labels:
    \begin{equation*}
      \begin{aligned}
        % & \Filter(\FromLabelTo{S}{a}{A}) & = 1 - \TransitionVar_6 \\
        % & \Filter(\FromLabelTo{S}{b}{B}) & = \TransitionVar_4 + \TransitionVar_6 \\
        % & \Filter(\FromLabelTo{A}{c}{A})  & = \TransitionVar_3  \\
        % & \Filter(\FromLabelTo{B}{b}{S}) & = 2\TransitionVar_6 + \TransitionVar_4 \\
        % & \Filter(\FromLabelTo{A}{a}{F}) & = 1 - \TransitionVar_6 \\
        % & \Filter(\FromLabelTo{B}{c}{F}) & = \TransitionVar_6 \\
        % Other automaton
        & \Filter(\FromLabelTo{S}{\Sigma}{S}) & = \VectorLiteral{\TransitionVar_{7a}, \TransitionVar_{7b}, \TransitionVar_{7c}} \\
        & \Filter(\FromLabelTo{S}{c}{F}) & = 1 \\
        & \Filter(\FromLabelTo{F}{\Sigma}{F}) & = \VectorLiteral{\TransitionVar_{9a}, \TransitionVar_{9b}, \TransitionVar_{9c}} \\
      \end{aligned}
    \end{equation*}

@@

    \begin{matrix}
      1 = \TransitionVar_{10} \land 
      \TransitionVar_3 = \TransitionVar_{11} \land \\
      1 = \TransitionVar_{12} \land 
      1 = \TransitionVar_{11} \land 
      2 > 0
    \end{matrix}  

@@

    \begin{matrix}
      1 = \TransitionVar_{10} \land 
      \TransitionVar_3 = \TransitionVar_{11} \land  \\
      1 = \TransitionVar_{12} \land 
      1 = \TransitionVar_{11} \land \\
      \Image{}_{\Automaton', \Map}(\Filter, 
      \VectorLiteral{2, 0, 1}) \land 
      \Connected(\SomethingCSomething{}, \Filter) \land
        2 > 0
    \end{matrix}  

@@

    \begin{matrix}
      1 = \TransitionVar_{10} \land
      \TransitionVar_3 = \TransitionVar_{11} 
      1 = \TransitionVar_{12} \land
      1 = \TransitionVar_{11} \\
      \Image{}_{\Automaton', \Map}(\Filter, 

@@

        \TransitionVar_{7c} + \TransitionVar_{9c} + 1}) \land \\
        1 - \TransitionVar_6 > 0 \land
        \TransitionVar_4 = 0 \land
        \TransitionVar_3 > 0 \land
        2\TransitionVar_6 + \TransitionVar_4 = 0 \land \\

@@

          \TransitionVar_3} \land \\
      \Connected(\SomethingCSomething{}, \Filter) \land

@@

    \end{matrix}  

@@

    \begin{matrix}
      1 - \TransitionVar_6 > 0 \land
      \TransitionVar_4 = 0 \land
      \TransitionVar_3 > 0 \land
      2\TransitionVar_6 + \TransitionVar_4 = 0 \land \\

@@

          \TransitionVar_3} \land \\

@@

      \VectorLiteral{\TransitionVar_{7a} + \TransitionVar_{9a}, 0, \TransitionVar_{7c} + \TransitionVar_{9c} + 1}) \land \TransitionVar_{7a} + \TransitionVar_{9a} > 0
    \end{matrix}

@@

  \begin{matrix}

@@

    1 - \TransitionVar_6 > 0 \land

@@

    \TransitionVar_4 = 0 \land
    \TransitionVar_3 > 0 \land
    2\TransitionVar_6 + \TransitionVar_4 = 0 \land \\

@@

        \TransitionVar_3} \land \\

@@

    \begin{matrix}

@@

    \end{matrix}

>>>>

  % SUBSUME
  \Subsume &
  \inferrule{\SomeInequalities,\SomeClause}{\Connected(\Automaton, \Filter), \SomeInequalities, \SomeClause} &
  \Split{} and \Propagate{} cannot be applied \\
  \bottomrule
  \end{tabular}
  \caption{Derivation rules for one automaton.}\label{tbl:rules:single}
\end{table}
We use the symbolic function $\FlowEq(\Automaton, \Filter)$ that generates a set
of existentially quantified linear inequalities with the following definition,
where we assign fresh, existentially quantified variables to
$\FinalStateVar_\State, \Filter(\Transition)$ for every $\State \in
\AcceptingStates, \Transition \in \Transitions$:
\[
\begin{aligned}
  \FlowEq(\Automaton, \Filter) &= \sum\limits_{\State \in \AcceptingStates} \FinalStateVar_\State = 1 \land \AndComp{\State \in \States}{\In(\State, \Filter) - \Out(\State, \Filter)} = \Sink(\State) \land
  \AndComp{\State \in \AcceptingStates}{\FinalStateVar_\State \geq 0}\\
  \Sink(\State) & = 0 \text{ if } \State \not\in \AcceptingStates, \FinalStateVar_\State \text{ otherwise.} \\
  \In(\State, \Filter) & = \StartFlow(\State) + \sum_{\Transition \in \FromLabelTo{\State'}{}{\State}} \Filter(\Transition)\\
  \StartFlow(\State)  &= 1 \text{ if } \State = \InitialState, \text{ otherwise $0$.} \\
  \Out(\State, \Filter) &= \sum_{\Transition \in \FromLabelTo{\State}{}{\State'}} \Filter(\Transition)
\end{aligned}
\]

@@

\begin{figure}[ht]
  We define $\Filter$ and $\FlowEq(\AcaOrBc{}, \Filter)$ as in the following two
  equations, and then apply \EquationReasoning{} (under the implicit assumption
  that every RHS is $\geq 0$) to obtain the third definition:
  \begin{minipage}[b]{0.3\linewidth}
    \begin{equation*}
      \begin{aligned}
        \Filter(\FromLabelTo{S}{a}{A}) & = \TransitionVar_1 \\
        \Filter(\FromLabelTo{S}{b}{B}) & = \TransitionVar_2 \\
        \Filter(\FromLabelTo{A}{c}{A}) & = \TransitionVar_3  \\
        \Filter(\FromLabelTo{B}{b}{S}) & = \TransitionVar_4 \\
        \Filter(\FromLabelTo{A}{a}{F}) & = \TransitionVar_5 \\
        \Filter(\FromLabelTo{B}{c}{F}) & = \TransitionVar_6 \\
      \end{aligned}
    \end{equation*}    
  \end{minipage}
  \hspace{0.5cm}
  \begin{minipage}[b]{0.3\linewidth}
    \begin{equation*}
      \begin{aligned}
        % S
        \TransitionVar_4 &= \TransitionVar_5 + \TransitionVar_2 - 1 \\
        % A
        \TransitionVar_1 &= \TransitionVar_5 \\
        % B
        \TransitionVar_2 &= \TransitionVar_4 + \TransitionVar_6 \\
        % F
        \TransitionVar_5 + \TransitionVar_6 &= \FinalStateVar_1 \\
        \FinalStateVar_1 &= 1 \\
      \end{aligned}  
    \end{equation*}    
  \end{minipage}
  \begin{minipage}[b]{0.3\linewidth}
    \begin{equation*}
      \begin{aligned}
        \Filter(\FromLabelTo{S}{a}{A}) & = 1 - \TransitionVar_6 \\
        \Filter(\FromLabelTo{S}{b}{B}) & = \TransitionVar_4 + \TransitionVar_6 \\
        \Filter(\FromLabelTo{A}{c}{A})  & = \TransitionVar_3  \\
        \Filter(\FromLabelTo{B}{b}{S}) & = 2\TransitionVar_6 + \TransitionVar_4 \\
        \Filter(\FromLabelTo{A}{a}{F}) & = 1 - \TransitionVar_6 \\
        \Filter(\FromLabelTo{B}{c}{F}) & = \TransitionVar_6 \\
      \end{aligned}
    \end{equation*}    
  \end{minipage}
  \caption{Equivalences defining $\Filter$ and $\FlowEq(\AcaOrBc{}, \Filter)$
  respectively.}\label{fig:example:single:equivalences}
  \end{figure}

\begin{figure}
  \centering
\begin{prooftree}
  \hypo[]{
{    \begin{array}{lll}
      1 - \TransitionVar_6 = 0 & \land \TransitionVar_6 = 1 & \land  \TransitionVar_4 + 1 > 0 \\
      \land \TransitionVar_3 = 0 &\land  2 + \TransitionVar_4 > 0 & \land k = 1 + \TransitionVar_4 
    \end{array}}
  }
  \infer1[\Subsume{}]{
{    \begin{array}{lll}
      \Connected(\AcaOrBc{}, \Filter) & \land 1 - \TransitionVar_6 = 0 \\
      \land \TransitionVar_6 = 1 & \land \TransitionVar_4 + 1 > 0 \land \\
      \land \TransitionVar_3 = 0 & \land 2 + \TransitionVar_4 > 0 \land \\
      k = 1 + \TransitionVar_4 
    \end{array}}
  }
  \infer1[\Propagate]{
    \begin{aligned}
      \Connected(\AcaOrBc{}, \Filter) \land \\
      1 - \TransitionVar_6 = 0 \land \\
      \TransitionVar_6 = 1 \land \\
      \TransitionVar_4 + 1 > 0 \land \\
      \TransitionVar_3 \geq 0 \land \\
      2 + \TransitionVar_4 \geq 0 \land \\
      2k = 2 + 2\TransitionVar_4 + \TransitionVar_3
    \end{aligned}
  }
  \infer1[\EquationReasoning{}]{
    \begin{aligned}
      \Connected(\AcaOrBc{}, \Filter) \land \\
      1 - \TransitionVar_6 = 0 \land \\
      2k = 1 + 2\TransitionVar_4 + \TransitionVar_3 + \TransitionVar_6
    \end{aligned}
  }
  % BRANCH:  = 0'
  \hypo{
    {\begin{array}{lll}
      \TransitionVar_3 > 0 & \land 
      \TransitionVar_6 = 0 \\ \land
      2\TransitionVar_6 + \TransitionVar_4 = 0 & \land
      1 - \TransitionVar_6 > 0\\  \land 
      2k = 1 + \TransitionVar_3
    \end{array}}
  }
  \infer1[\Subsume{}]{
    \begin{aligned}
      \Connected(\AcaOrBc{}, \Filter) \land \\
      \TransitionVar_3 > = 0 \land \\
      \TransitionVar_6 = 0 \land \\
      2\TransitionVar_6 + \TransitionVar_4 = 0 \land \\
      1 - \TransitionVar_6 > 0 \land \\
      2k = 1 + \TransitionVar_3
    \end{aligned}
  }
  \infer1[\EquationReasoning{}]{
    \begin{aligned}
      \Connected(\AcaOrBc{}, \Filter) \land \\
      \TransitionVar_6 = 0 \land \\
      1 - \TransitionVar_6 > 0 \land \\
      2\TransitionVar_6 + \TransitionVar_4 = 0\\
      2k = 1 + 2\TransitionVar_4 + \TransitionVar_3
    \end{aligned}
  }
  \infer1[\Propagate{}]{
    \begin{aligned}
      \Connected(\AcaOrBc{}, \Filter) \land \\
      \TransitionVar_6 = 0 \land \\
      1 - \TransitionVar_6 > 0 \land \\
      2k = 1 + 2\TransitionVar_4 + \TransitionVar_3
    \end{aligned}
  }
  \infer1[\EquationReasoning{}]{
    \begin{aligned}
      \Connected(\AcaOrBc{}, \Filter) \land \\
      1 - \TransitionVar_6 > 0 \land \\
      2k = 1 + 2\TransitionVar_4 + \TransitionVar_3 + \TransitionVar_6
    \end{aligned} % BRANCH: > 0
  } % SPLIT
  \infer2[\Split{} $1 - \TransitionVar_6$]{ \Connected(\AcaOrBc{}, \Filter) \land 2k = 1 + 2\TransitionVar_4 + \TransitionVar_3 + \TransitionVar_6 }
  \infer1[\EquationReasoning{}]{
    \Connected(\AcaOrBc{}, \Filter) \land
    2k + 1 =
    \sum\limits_{\Transition \in \Transitions} (\Transition \mapsto 1)(\Label) \cdot \Filter(\Transition)
  }
  \infer1[\Expand{}]{\Image{}_{\AcaOrBc{}, \Transition \mapsto 1}(\Filter, 2k + 1)}
\end{prooftree}
\caption{A derivation for \Calculus{} computing odd lengths in $\AcaOrBc{}$.}\label{fig:derivation:single}
\end{figure}

@@

In the interest of space, we refer back to
\cref{fig:example:single:equivalences} for the definitions of $\Filter$ for
$\AcaOrBc$ and only define $\Filter$ for $\SomethingCSomething{}$ after
substitutions as follows. Note the expansion of the $\Sigma$ labels:
    \begin{equation*}
      \begin{aligned}
        % & \Filter(\FromLabelTo{S}{a}{A}) & = 1 - \TransitionVar_6 \\
        % & \Filter(\FromLabelTo{S}{b}{B}) & = \TransitionVar_4 + \TransitionVar_6 \\
        % & \Filter(\FromLabelTo{A}{c}{A})  & = \TransitionVar_3  \\
        % & \Filter(\FromLabelTo{B}{b}{S}) & = 2\TransitionVar_6 + \TransitionVar_4 \\
        % & \Filter(\FromLabelTo{A}{a}{F}) & = 1 - \TransitionVar_6 \\
        % & \Filter(\FromLabelTo{B}{c}{F}) & = \TransitionVar_6 \\
        % Other automaton
        \Filter(\FromLabelTo{S}{\Sigma}{S}) & = \VectorLiteral{\TransitionVar_{7a}, \TransitionVar_{7b}, \TransitionVar_{7c}} \\
        \Filter(\FromLabelTo{S}{c}{F}) & = 1 \\
        \Filter(\FromLabelTo{F}{\Sigma}{F}) & = \VectorLiteral{\TransitionVar_{9a}, \TransitionVar_{9b}, \TransitionVar_{9c}} \\
      \end{aligned}
    \end{equation*}

@@

    {\begin{array}{lll}
      1 = \TransitionVar_{10} & \land \TransitionVar_3 = \TransitionVar_{11} & \land 1 = \TransitionVar{12} \\ 
      \land 1 = \TransitionVar_{11} &  & \land 2 > 0
    \end{array}}  

@@

    {\begin{array}{ll}
      2 > 0 \land 1 = \TransitionVar_{10} & \land \TransitionVar_3 = \TransitionVar_{11} \\
      \land 1 = \TransitionVar_{12} & \land 1 = \TransitionVar_{11} \\
      \land \Image{}_{\Automaton', \Map}(\Filter, \VectorLiteral{2, 0, 1}) & \land \Connected(\SomethingCSomething{}, \Filter) \\
    \end{array}}  

@@

  {  \begin{array}{ll}
      1 = \TransitionVar_{10} \land \TransitionVar_3 = \TransitionVar_{11} & 
      \land 1 = \TransitionVar_{12} \land 1 = \TransitionVar_{11} \\
      \land \Image{}_{\Automaton', \Map}(\Filter, 

@@

        \TransitionVar_{7c} + \TransitionVar_{9c} + 1}) & \land 
        \TransitionVar_6 + \TransitionVar_4 = 0 \\
        \land 1 - \TransitionVar_6 > 0 \land \TransitionVar_6 = 0 &
        \land \TransitionVar_4 = 0 \land  \TransitionVar_3 > 0 \\
        \land 2\TransitionVar_6 + \TransitionVar_4 = 0 & \land 

@@

          \TransitionVar_3} \\ \land 
      \Connected(\SomethingCSomething{}, \Filter) &

@@

    \end{array} } 

@@

    {\begin{array}{ll}
      \TransitionVar_6 + \TransitionVar_4 = 0 \land 1 - \TransitionVar_6 > 0 &
      \land \TransitionVar_6 = 0  \land \TransitionVar_4 = 0 \\
      \land \TransitionVar_3 > 0 & \land 2\TransitionVar_6 + \TransitionVar_4 = 0 \\
      \land 

@@

          \TransitionVar_3} & \land
      \Connected(\SomethingCSomething{}, \Filter) \\
      \land 

@@

      \VectorLiteral{\TransitionVar_{7a} + \TransitionVar_{9a}, 0, \TransitionVar_{7c} + \TransitionVar_{9c} + 1}) & \land \TransitionVar_{7a} + \TransitionVar_{9a} > 0
    \end{array}}

@@

  {\begin{array}{ll}

@@

    1 - \TransitionVar_6 > 0 &
    \land

@@

    \TransitionVar_4 = 0 \\
    \land
    \TransitionVar_3 > 0 & \land
    2\TransitionVar_6 + \TransitionVar_4 = 0 \\ 
    \land

@@

        \TransitionVar_3} & \land 
    \Connected(\AcaOrBc{}, \Filter) \\
    \land 
    \Connected(\SomethingCSomething{}, \Filter) \\
    \land 

@@

    \begin{aligned}

@@

    \end{aligned}
